\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/experiment.tex
minor experiment edits
edits. `

During the experiment of privacy extraction via our video capture mode, we chose \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, a
smartphone in \mbox{EMUI 11.0.0.135(C00E128R2P5)} \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the
target device. In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of \ac{OCR}  to
extract text from corresponding video frames. In this experiment, the attacker
successfully extracted text such as name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and performs transactions
without the password. During our experiment, we noticed that this HUAWEI device supports `Desktop Mode'
for its external screen, which enables user to use their devices like a desktop computer with a external screen.
If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary screen, as we discussed in Section~\ref{subsec:attack_init}.
As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

@@

\subsection{Case study}
\label{subsec:case_study}
\tool can be used in various attack scenarios, ranging from mobile devices to PC devices.
For example, \tool can be attached to the power station, which provides USB 3.x hubs, in the airport to perform attacks.
Most people charge their laptops or smartphones in the power station in emergency, with negligence of security.
In the following paragraphs, we will demonstrate the attack scenarios of \tool using sharing power bank as an example.

@@

\subsubsection{Result}
In summary, \tool is able to actively obtain most sensitive information from the screen, such as browsing history, personal account, phone number without victim's interaction. There also exists information such as payment password that is not available immediately, but such a piece of information can be obtained once the victim inputs it. The obtained information can be further used to guess the victim's lock screen password and poses even greater threat to victim's privacy.

>>>>

During the experiment of privacy extraction via our video capture mode, we chose \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, a
smartphone in \mbox{EMUI 11.0.0.135(C00E128R2P5)} \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the
target device. In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of \ac{OCR}  to
extract text from corresponding video frames. In this experiment, the attacker
successfully extracted text such as name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and performs transactions
without the password. During our experiment, we noticed that this HUAWEI device supports `Desktop Mode'
for its external screen, which enables user to use their devices like a desktop computer with an external screen.
If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary screen, as we discussed in Section~\ref{subsec:attack_init}.
As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

@@

\subsection{Case study}
\label{subsec:case_study}
\tool can be used in various attack scenarios, ranging from mobile devices to PC devices.
For example, \tool can be attached to the power station, which provides USB 3.x hubs, in the airport to perform attacks.
Most people charge laptops or smartphones in the power station in emergency, with negligence of security.
In the following paragraphs, we will demonstrate the attack scenarios of \tool using sharing power bank as an example.

@@

\subsubsection{Result}
In summary, \tool is able to actively obtain most sensitive information from the screen, such as browsing history, personal account, phone number without victim's interaction. There also exists information such as payment password that is not available immediately, but such a piece of information can be obtained once the victim inputs it. The obtained information can be used to guess the victim's lock screen password and poses further threat to victim's privacy.
